Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-29 docs/00-manuscripts/ieee/ieee-manuscript.tex
revewrite methods: feature importance calc

\noindent A spatial nested cross-validation on the plot level was chosen to reduce the influence of spatial autocorrelation as much as possible \cite{schratz2019, sperrorest}.
The \ac{RMSE} was chosen as the error measure.
Each plot served as one fold within the cross-validation setting, resulting in four iterations in total.
For the inner level (hyperparameter tuning), \(k - 1\) folds were used with \(k\) being the number of plots.

@@

\noindent Estimating feature importance for highly-correlated datasets is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features \cite{molnar2019}.
Methods like \ac{PDP} or permutation-based approaches do not produce reliable estimates in such scenarios because unrealistic combinations between covariates are created \cite{molnar2019}.
Permutation feature importance calculates the loss of predictive performance for each feature by permuting it in a random manner during prediction.
The more important the feature is for the model, the higher the mean loss in the measure, reflecting the importance of the specific feature for the current model.
Predicting and calculating the error measure multiple times per feature comes with some computational cost.
For increased efficiency, we estimated the feature importance only for datasets HR and VI using the best performing learner of the benchmark.

However, as of today there are no unbiased approaches for estimating feature importance for (highly) correlated datasets.
Nevertheless, recent methods like \ac{ALE} plots aim to tackle this problem by utilizing marginal distributions of features over a small window to focus on the effect of a single feature \cite{apley2019, molnar2019}.
However, ALE plots need visual inspection and as the number of features increases, making objective comparisons/conclusions becomes challenging.

In this work we applied permutation-based feature importance and \ac{ALE} plots (HR only) to estimate feature importance.
With the limitations of both methods in mind we aimed to get a general overview of the feature importance of the hyperspectral bands while trying to avoid the over-interpretation of results.
We used the best-performing algorithm on the HR task (i.e. SVM) to calculate the feature importance.

>>>>

A spatial nested cross-validation on the plot level was chosen to reduce the influence of spatial autocorrelation as much as possible \cite{schratz2019, sperrorest}.
The \ac{RMSE} was chosen as the error measure.
Each plot served as one fold within the cross-validation setting, resulting in four iterations in total.
For the inner level (hyperparameter tuning), \(k - 1\) folds were used with \(k\) being the number of plots.

@@

Estimating feature importance for datasets with highly-correlated features is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features \cite{molnar2019}.
Methods like \ac{PDP} or permutation-based approaches may produce unreliable estimates in such scenarios because unrealistic situations between covariates are created \cite{molnar2019}.
Estimating feature importance for machine learning methods is a complicated procedure for which many different approaches, model-specific and agnostic, exist \cite{friedman2001, hastie2001, greenwell2018}.
The development of robust methods which enable an unbiased estimation of feature importance for highly-correlated variables are subject to current research.

In this work permutation-based feature importance and \ac{ALE} plots (HR only) were calculated to estimate feature importance / effects \cite{apley2019, molnar2019}.
With the limitations of both methods in mind when applied to correlated features, the aim was to get a general overview of the feature importance of the hyperspectral bands while trying to avoid an over-interpretation of results.
The best-performing algorithm on the HR task (i.e. SVM) was used for the feature importance calculation.
